Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex
abstract

\begin{figure}[htpb]
	\capstart
	\centerline{{\includegraphics[width=.3\linewidth]{typeconeFan}}\hspace{1.5cm}\includegraphics[width=.4\linewidth]{typecone}}
	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones $a,\dots, e$. We depict the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional slice. On top of each face of $\ctypeCone(F)$, and example of polytope with the corresponding normal fan is depicted.}
	\label{fig:typecone}
\end{figure}
\end{example}

>>>>

\begin{figure}[htpb]
	\capstart
	\centerline{{\includegraphics[scale=1]{typeconeFan}}\hspace{1.5cm}\includegraphics[width=.4\linewidth]{typecone}}
	\caption{A complete $2$-dimensional fan~$\Fan$ with five rays $v_1,\dots,v_5$ and five maximal cones~$a,\dots, e$ (left), and the intersection of $\b{K}\ctypeCone(F)$ with a hyperplane to get a $2$-dimensional slice (right). On top of each face of $\ctypeCone(F)$, we depict an example of polytope with the corresponding normal fan.}
	\label{fig:typecone}
\end{figure}
\end{example}
